---
title: "AuSSA 1979"
author: "Samantha Richins"
date: "May 29, 2022"
output: 
  html_document:
    keep_rmd: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
```



## Research Question

Is there a correlation between political party preference and acquired institutional education?


## Data

The Australian Survey of Social Attitudes (AUSSA 1979) 

[Data Link](https://dataverse.ada.edu.au/dataset.xhtml?persistentId=doi:10.26193/AIOCOR)


## Variables 

### Independent

Institutional Educational Attainment 

 - Has bachelors degree
 
 - Does not have bachelors degree


### Dependent

Political Party Affiliation

 - Labor Party (LAP)
 
 - Liberal Party
 
 - National (Country) Party
 
 - Australian Democrat
 
 - No Party Affiliation
 
 - Other Party (Not Listed)

---

## Graph


```{r include=FALSE}
AUpas_1979 <- read.csv("AUpolitical_attitudes_survey_1979.csv") %>% 
  select(c(PYAFFL79, EDUCAT79))

AUpas_79 <- AUpas_1979 %>% 
  mutate(education = case_when(
      EDUCAT79 <= 7 ~ "No BA",
      EDUCAT79 == 8 ~ "Has BA"),
    political_affiliation = case_when(
      PYAFFL79 == 0 ~ "NA",
      PYAFFL79 == 1 ~ "Liberal Party",
      PYAFFL79 == 2 ~ "Labor Party (LAP)",
      PYAFFL79 == 3 ~ "National (Country) Party",
      PYAFFL79 == 4 ~ "Australian Democrat",
      PYAFFL79 == 5 ~ "Other",
      PYAFFL79 == 6 ~ "No Affiliation",
      PYAFFL79 == 7 ~ "NA",
      PYAFFL79 == 8 ~ "NA"
    ))

```


```{r echo=FALSE}
ggplot(AUpas_79) +
  geom_bar(aes(y = political_affiliation, color = education))
```

---

## Table

```{r echo=FALSE}
table(AUpas_79$political_affiliation, AUpas_79$education) %>% 
  pander::pander()
```

